Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-05-29 tex/VHzQ.tex
VHzQ.tex update

>>>>

At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.

Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).

Then calculate the clipped median and standard deviation, 
\begin{equation}
1.48 \times \sigma_{median} / \bar{epsilon}
\end{equation}
where $\bar{epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
%%
With this definition, although some of the objects have very well sampled, 
`Average' light curves where you are averaging over e.g. a month, or two weeks.

Longer time-series, better SNR and moreover, $(1+z)$. 
Just selecting things that would
%%
Doing this independtly in each band...
%Variation

%% 
%% Object numbers: 54 VSA   MMTJ0215-0529,
%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
%%
objiD 164 is SDSSJ1000+0234, faint; very faint. 
SHELLQsJ0220-0432: (qso59) show this too. 
CFHQSJ0216-0455
